`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-06-16 inst/manuscript/manuscript.rmd
Split figure into 2: one for traces, one for PPR plots;

figure1 <- multi_panel_figure(
  widths = rep(17.22/3-2*0.25, 3), 
  heights = rep(27/7-5*0.25, 7), 
  unit = "cm",
  inter_row_spacing = c(0, rep(0.5, 6)),
  inter_column_spacing = c(0, rep(0.5, 2)))

@@

Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
alignment to the time of dithionite addition is employed (default) as well as 
custom trimming of the time axis to account for divergent acquisition 
times between experiments. PPR scaling is used with the default factor of 0.65.

```{r noeval_demonstrate_traces, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces(
  "inputTable.txt",
  time_max_sec = 350)
```

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_perturbed_submitted.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- tmpDir %>%
  file.path("inputTable.txt") %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 3,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])) +
    facet_wrap(c("`Experimental Series`"))+
    guides(colour = "none"))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot(
  "inputTable.txt",
  generation_of_algorithm = 2) +
xlim(0, 2)
```

@@

The call results in the protein to phospholipid ratio (PPR) plot shown in
Figure 1B. Using the customization facilities provided by `ggplot2` 
[@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
avoid visual compression of all data by a single data point from the wild type 
rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$. Dashed lines
are added automatically as graphical representations of the fit constant 
$\alpha$.

Figure 1B emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C/D by
@ploier_perturbed_submitted, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 1C:

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot(
  "inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 1C
by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved
and produces tabular output represented in Table 1.

>>>>

divisor <- 20
figure2 <- multi_panel_figure(
  widths = rep(17.22), 
  heights = c(
    18/divisor * 7 - 0.25,
    18/divisor * 13 - 0.25), 
  unit = "cm",
  inter_row_spacing = 0.5,
  inter_column_spacing = 0.5)

@@

Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
step plots the corresponding spectral traces (Figure 1). Note that algorithmic
alignment to the time of dithionite addition is employed (default) as well as 
custom trimming of the time axis to account for divergent acquisition 
times between experiments. PPR scaling is used with the default factor of 0.65.

```{r noeval_demonstrate_traces, eval = FALSE}
# Plot spectral traces (Figure 1)
scramblase_assay_traces(
  "inputTable.txt",
  time_max_sec = 350)
```

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_perturbed_submitted.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- tmpDir %>%
  file.path("inputTable.txt") %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
scramblase_assay_traces(
  x,
  time_max_sec = 350)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 2A)
scramblase_assay_plot(
  "inputTable.txt") +
xlim(0, 2)
```

```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2 %<>% add_panel(
  top_panel = 1,
  panel = scramblase_assay_plot(x) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure2 %<>% add_panel(
  top_panel = 2,
  panel = scramblase_assay_plot(x, split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])) +
    facet_wrap(c("`Experimental Series`"))+
    guides(colour = "none"))
figure2
```

@@

The call results in the protein to phospholipid ratio (PPR) plot shown in
Figure 2A. Using the customization facilities provided by `ggplot2` 
[@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
avoid visual compression of all data by a single data point from the wild type 
rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$. Dashed lines
are added automatically as graphical representations of the fit constant 
$\alpha$.

Figure 2A emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C/D by
following more closely the analysis in Figure 4C--F by
@ploier_perturbed_submitted, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 2B:

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 2B)
scramblase_assay_plot(
  "inputTable.txt",
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 2B
by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved
and produces tabular output represented in Table 1.
